---
title: "cendog"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cendog}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(cendog)
```

The cendog package replicates the central dogma of molecular biology. It consists of 5 functions. 

Function 1: DNA_sample

This function generates a random DNA sequence of a specified length. The sequence consists of the nucleotides A, T, G and C, which are the building blocks of DNA. The function accepts the input from one parameter, amount_nucleotides, which contains the desired length of the DNA sequence. By using sample(), the function randomly selects nucleotides and replacement equals true, so nucleotides can appear multiple times. This generates a vector DNA_nucleotides of random DNA bases. These nucleotides are then combined into a single string as all elements are joined without spaces to form a continuous DNA sequence.



Function 2: DNA_to_RNA
This function, named DNA_to_RNA, is designed to convert a DNA sequence (provided as the input DNA1) into an RNA sequence by replacing thymine (T) with uracil (U). The output of the function, RNA1, is the RNA sequence equivalent to the input DNA sequence, DNA1.



Function 3: make_codon
This function takes a nucleotide sequence (e.g. “ATGCGT”) and divides it into codons, each consisting of three nucleotides. The function has a start parameter, that defines the starting positions for reading the codons. Hereafter, the function calculates the length of the nucleotide sequence and saves the number as ‘num_nucleotides’. The function generates codons by generating a sequence of starting positions for each codon, starting at the ‘start’ position defined and moving three characters ahead. The ending positions for each codon are three characters after the corresponding starting position. The function returns a vector containing the codons generated from the input nucleotide sequence. 







